---
title: "ABC"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"ABC"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r}

library(mclust)
library(TestPackage12)

#MyVignette

xassetCountrySector <- read.table('~/TestPackage12/extdata/format.out.Heliconius2',  sep="\t", header=TRUE, as.is=TRUE)
  GFF <- read.table('~/TestPackage12/extdata/gff_parser.out.Heliconius2',  sep="\t", header=TRUE, as.is=TRUE)
  gene.chr.match <- GFF[match(xassetCountrySector$Gene, GFF$Gene), ]
  counts.head   <- as.matrix(round(xassetCountrySector[3:ncol(xassetCountrySector)] ))
  Groupings <- rep("X", ncol(xassetCountrySector)-2 )
  segLengths <- xassetCountrySector$Len
  cd.head <- new("countData", data = counts.head, replicates = Groupings, groups = list(Groupings, Groupings), annotation = gene.chr.match, seglens = segLengths  )
  libsizes(cd.head) <-   getLibsizes(cd.head,   estimationType = "edgeR")
OBJ <- cd.head 

OBJ@replicates<- as.factor(c("F","F", "F", "M", "M", "M","M", "M", "M", "M", "M","M", "F", "F", "F", "F","F", "F", "F", "F", "M","M", "F","F", "F", "F","M", "M", "F", "F", "F","F", "M", "M", "M", "M","M", "M", "M", "M", "F","F", "F", "F", "M", "M","M", "M", "F", "F", "F","F", "F", "F", "M", "M","M", "M"))
OBJ@RPKM<- make_RPKM(OBJ)

OBJ@annotation$something <- (gene.chr.match$Chr == "Z")
OBJ@annotation$something[OBJ@annotation$something==TRUE] <- "Z"
OBJ@annotation$something[OBJ@annotation$something==FALSE | is.na(OBJ@annotation$something)] <- "A"

## Factorized anntoation column input:
OBJ@annotation$something <- factor(x = OBJ@annotation$something, levels = c("A", "Z"))

CYD_AB<- OBJ[,c(39,41,43,45,47,49,51,53,55,57)]
CYD_HD <- OBJ[,c(40,42,44,46,48,50,52,54,56,58)]

plotExpr(CYD_AB, col=c("black","red","black","red"), notch=T, outline=FALSE, cex.axis=0.8, mode_mean=FALSE, LOG2=TRUE, clusterby_grouping=FALSE, groupings="something")

# REMOVING 28%
f_CYD_AB <- dafsFilterWrapper(CYD_AB)
plotExpr(f_CYD_AB, col=c("black","red","black","red"), notch=T, outline=FALSE, cex.axis=0.8, mode_mean=FALSE, LOG2=TRUE, clusterby_grouping=FALSE, groupings="something")

# REMOVING 56%
f_CYD_AB <- quantFilter(CYD_AB, 0.2) 
plotExpr(f_CYD_AB, col=c("black","red","black","red"), notch=T, outline=FALSE, cex.axis=0.8, mode_mean=FALSE, LOG2=TRUE, clusterby_grouping=FALSE, groupings="something")

# REMOVING 71%
f_CYD_AB <- iqrxFilter(CYD_AB, IQR_MULTIPLIER=1)
plotExpr(f_CYD_AB, col=c("black","red","black","red"), notch=T, outline=FALSE, cex.axis=0.8, mode_mean=FALSE, LOG2=TRUE, clusterby_grouping=FALSE, groupings="something")

outlist <- generateStats(f_CYD_AB, groupings="something", mode_mean=TRUE)
outlist$kruskal
outlist$summary

outlist <- test_diffs(f_CYD_AB, groupings="something", mode_mean=TRUE,  treatment1="M", treatment2="F")
outlist$kruskal
outlist$summary

plotRatioBoxes(f_CYD_AB, treatment1="M", treatment2="F", groupings="something", cex.axis=0.8, outline=FALSE)

plotRatioDensity(f_CYD_AB, treatment1="M", treatment2="F", mode_mean=TRUE, LOG2=TRUE, col =c("black","red"), lty = 1, type = "l", groupings="something")




```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
